PACE Solver Description: OCMu64,\\ a solver for One-sided Crossing Minimization

### 2024-09-20 tex/paper.tex
More small changes.

  We introduce the novel \emph{strongly fixed}, \emph{practically fixed}, and
  \emph{practically glued} reductions that maximally generalize some existing
  reductions.
  We apply these in our exact solver OCMu64, that directly uses branch-and-bound
  on the ordering of the vertices of $B$ and does not depend on ILP or SAT
  solvers.
\end{abstract}

@@

The 2024 edition of PACE, an annual optimization challenge, considers the
\emph{one-sided crossing minimization} problem, defined as follows.
Given is a bipartite graph $(A, B)$ that is drawn in the plane at points
$(i, 1)$ and $(j,0)$ for components $A$ and $B$ respectively. The ordering of $A$
is fixed, and the goal is the find an ordering of $B$ that minimizes the number of
crossings when edges are drawn as straight lines.

@@

\begin{figure}[t]
\centering
\hfill
\subfloat[An instance of \cref{lem:weak}.]{
\includegraphics[width=0.30\textwidth]{fig/simple.pdf}%
\label{fig:simple}
}
\hfill
\subfloat[Examples of blocking sets (\cref{pfp}), preventing $u\b v$.]{
\includegraphics[width=0.6\textwidth]{fig/blocking-set.pdf}%
\label{fig:blocking}
}
\hfill
\\
\subfloat[Examples of strongly fixed pairs (\cref{def:sfp}).]{
\includegraphics[width=0.9\textwidth]{fig/strongly-fixed.pdf}%
\label{fig:strongly-fixed}
}
%% \subfloat[]{
%% \includegraphics[width=0.33\textwidth]{fig/gluing.pdf}%
%% \label{fig:gluing}
%% }
\caption{
  Various examples where $u$ must come before $v$ ($u\b v$), where $u,v\in B$ can freely move around and
  their neighbours in $A$ (on the dashed line) have fixed positions.}%
\label{fig}
\end{figure}

>>>>

  We introduce the novel \emph{strongly fixed}, \emph{practically fixed}, and
  \emph{practically glued} reductions that maximally generalize some existing
  reductions.
  We apply these in our exact solver \texttt{OCMu64}, that directly uses branch-and-bound
  on the ordering of the vertices of $B$ and does not depend on ILP or SAT
  solvers.
\end{abstract}

@@

The 2024 edition of PACE, an annual optimization challenge, considers the
\emph{one-sided crossing minimization} problem, defined as follows.
Given is a bipartite graph $(A, B)$ that is drawn in the plane at points
$(i, 0)$ and $(j,1)$ for components $A$ and $B$ respectively. The ordering of $A$
is fixed, and the goal is the find an ordering of $B$ that minimizes the number of
crossings when edges are drawn as straight lines.

@@

\begin{figure}[t]
\centering
\hfill
\subfloat[An instance of \cref{lem:weak}.]{
\includegraphics[width=0.30\textwidth]{fig/simple.pdf}%
\label{fig:simple}
}
\hfill
\subfloat[Examples of blocking sets (\cref{pfp}), preventing $u\b v$.]{
\includegraphics[width=0.6\textwidth]{fig/blocking-set.pdf}%
\label{fig:blocking}
}
\hfill
\\
\subfloat[Examples of strongly fixed pairs (\cref{def:sfp}).]{
\includegraphics[width=0.9\textwidth]{fig/strongly-fixed.pdf}%
\label{fig:strongly-fixed}
}
%% \subfloat[]{
%% \includegraphics[width=0.33\textwidth]{fig/gluing.pdf}%
%% \label{fig:gluing}
%% }
\caption{
  Various examples of $u, v \in B$, whose neighbors 
  neighbours in $A$ (on the dashed line) have fixed positions.}%
\label{fig}
\end{figure}
